---
title: "Collared Pika Distance Sampling Analysis"
author: "Jeff Wagner"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---
```{r echo=FALSE, results='hide', message=FALSE}
library(dplyr)
library(data.table)
library(tidyverse)
library(unmarked)
library(lubridate)
library(ggplot2)
library(readxl)
library(psych)
library(snotelr)
library(sf)
library(sp)
library(mapview)
library(lwgeom)
library(AICcmodavg)
library(spatialEco)
library(kableExtra)
library(grid)
library(gridExtra)
load("05_Environment.RData")
```

This is a breakdown of an analysis of collared pika *(Ochotona collaris)* data collected by the Alaska Center for Conservation Science in 2018-2019. The data was collected following a spatially-explicit distance sampling approach (Royle et al. 2004). Analysis was conducted in Program R (version 4.2.0) with package *unmarked* (version 1.2.5) and predictors were compiled via an ArcGIS Pro Python installation (version 3.6+).

### **Model Selection Table:**
```{r echo=FALSE}
knitr::kable(expMod.Selection, caption = "Table 1. AICc model selection table",
             col.names = c("Model", "K", "AICc", "Delta AICc", "Model Likelihood", "AICc Weight", 
                           "Log Likelihood", "Cumulative Weight")) %>% 
  kable_styling()
```

### *Climate & Productivity Model*
##### Summary and Parameter Estimates
```{r echo=FALSE}
summary(climateProductivity)
confint(climateProductivity, type = "state")
```

##### Goodness of fit
```{r echo=FALSE}
Nmix.gof.test(climateProductivity)
```

```{r echo=FALSE, message=FALSE, dpi=300, fig.width=8, fig.height=8, fig.fullwidth=TRUE}
plot.climateProductivity <- grid.arrange(arrangeGrob(plot.climateProductivityPrecip, plot.climateProductivitySummerWarmth,
                                         plot.climateProductivityJanuaryMinTemp, plot.climateProductivityNDVI,
                                         layout_matrix = matrix(c(1,2,3,4), byrow = TRUE, ncol = 2),
                                         left = textGrob(expression(
                                           paste("Denisty (Pika / km" ^ "2"*")")),
                                           rot = 90,  gp = gpar(fontsize = 14))))
```

### *Climate Model*
##### Summary and Parameter Estimates
```{r echo=FALSE}
summary(climate)
confint(climate, type = "state")
```

##### Goodness of fit
```{r echo=FALSE}
Nmix.gof.test(climate)
```

```{r echo=FALSE, message=FALSE,dpi=300, fig.width=8, fig.height=8, fig.fullwidth=TRUE}
plot.climate <- grid.arrange(arrangeGrob(plot.climatePrecip, plot.climateSummerWarmth,
                                         grid::nullGrob(), plot.climateJanuaryMinTemp, grid::nullGrob(),
                                          layout_matrix = matrix(c(1,1,2,2,3,4,4,5), byrow = TRUE, ncol = 4),
                                          left = textGrob(expression(
                                            paste("Denisty (Pika / km" ^ "2"*")")),
                                                         rot = 90,  gp = gpar(fontsize = 14))))
```

### *Productivity Model*
##### Summary and Parameter Estimates
```{r echo=FALSE}
summary(productivity)
confint(productivity, type = "state")
```
##### Goodness of fit
```{r echo=FALSE}
Nmix.gof.test(productivity)
```

```{r echo=FALSE, message=FALSE, dpi=300, fig.width=8, fig.height=8, fig.fullwidth=TRUE}
plot.productivity <- grid.arrange(arrangeGrob(plot.productivityNDVI, plot.productivityLOGS,
                                         grid::nullGrob(), plot.productivityWetness, grid::nullGrob(),
                                          layout_matrix = matrix(c(1,1,2,2,3,4,4,5), byrow = TRUE, ncol = 4),
                                          left = textGrob(expression(
                                            paste("Denisty (Pika / km" ^ "2"*")")),
                                                         rot = 90,  gp = gpar(fontsize = 14))))
```

### *Climate & Topography Model*
##### Summary and Parameter Estimates
```{r echo=FALSE}
summary(climateTopo)
confint(climateTopo, type = "state")
```

##### Goodness of fit
```{r echo=FALSE}
Nmix.gof.test(climateTopo)
```


```{r echo=FALSE, message=FALSE, dpi=300, fig.width=8, fig.height=8, fig.fullwidth=TRUE}
plot.climate <- grid.arrange(arrangeGrob(plot.climateTopoPrecip, plot.climateTopoSummerWarmth,
                                         plot.climateTopoJanuaryMinTemp, plot.climateTopoElevation,
                                         plot.climateTopoRoughness, plot.climateTopoNorthness,
                                          layout_matrix = matrix(c(1,2,3,4,5,6), byrow = TRUE, ncol = 2),
                                          left = textGrob(expression(
                                            paste("Denisty (Pika / km" ^ "2"*")")),
                                                         rot = 90,  gp = gpar(fontsize = 14))))
```


### *Model-Averaged Estimates*
```{r echo = FALSE}
knitr::kable(df, caption = "Table 2. Model-averaged coefficients",
             col.names = c("Parameter", "# of models", "Estimate", "SE", "Lower CL", "Upper CL")) %>% 
  kable_styling() %>%
  row_spec(c(1,2,4,6,8),bold=T,hline_after = T)
```

```{r echo=FALSE, message=FALSE, dpi=300, fig.width=8, fig.height=10, fig.fullwidth=TRUE}
plot.average <- grid.arrange(arrangeGrob(plot.avgPrecip, plot.avgSummerWarmth, plot.avgJanuaryMinTemp, 
                                         plot.avgLogs, plot.avgNDVI, plot.avgWetness,
                                         plot.avgRoughness, plot.avgElevation, plot.avgNorthness,
                                         grid::nullGrob(), plot.Location, grid::nullGrob(),
                                         layout_matrix = matrix(c(1,2,3,
                                                                  4,5,6,
                                                                  7,8,9,
                                                                  10,11,12), byrow = TRUE, ncol = 3),
                                         left = textGrob(expression(
                                           paste("Denisty (Pika / km" ^ "2"*")")),
                                           rot = 90,  gp = gpar(fontsize = 14))))
```
